
```{r}
library(tidyverse)
library(ggplot2)
library(stringr)

url<-"https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
destfile<-paste(getwd(),"exdata_data_NEI_data.zip",sep="/") 
download.file(url, destfile)
unzip(destfile)
data<-read.csv("activity.csv")

```
What is the mean number of steps taken per day?


This code creates a histogram plot of the total number of steps taken each day:
  
```{r message = FALSE, warning = FALSE}
sum<-data %>% group_by(date) %>% summarise(dailysteps = sum(steps))
ggplot(sum, aes(dailysteps)) + geom_histogram()
```


The code below provides the mean and median of steps each day


```{r message = FALSE, warning = FALSE}

mean<-mean(sum$dailysteps, na.rm = TRUE)
median<-median(sum$dailysteps,na.rm=TRUE)
```
                
The mean number of steps is `r mean` and the median is `r median`


What is the average daily activity pattern?

```{r warning = FALSE, message = FALSE}
data <-data %>% group_by(interval) %>% 
  mutate(average_steps = mean(steps, na.rm = TRUE))

ggplot(data, aes(interval, average_steps)) + geom_line()
```
Which 5-minute interval, average across all the days in the dataset, 
contains the maximum number of steps?

  ```{r}

max_interval<-data[which.max(data$average_steps),]

```
The interval with the maximum number of steps is `r max_interval`

Imputing missing values: 
1. Calculate and report the total number of missing values in the dataset 
(i.e. the total number of rows with NAs)
```{r}
missing_rows<-nrow(data %>% filter(is.na(steps)))
```
The number of rows with missing data is `r missing_rows`

In the following section, I replaced missing values with the average for 
that specific interval across all other days. 

```{r}
test <- function(x, y, z) {
  if(is.na(x)==TRUE) y else z
}

data$finalsteps <- mapply(test, data$steps, data$average_steps, data$steps)

```

This is the plot of daily steps using imputted values
```{r}
sum2<-data %>% group_by(date) %>% summarise(dailysteps = sum(finalsteps))
ggplot(sum2, aes(dailysteps)) + geom_histogram()
```
```{r message = FALSE, warning = FALSE}

mean<-mean(sum2$dailysteps, na.rm = TRUE)
median<-median(sum2$dailysteps,na.rm=TRUE)
```
                
Using the dataset with imputed data, the mean number of steps is `r mean` and the median is `r median`


Are there differences in activity patterns between weekdays and weekends?
```{r}
data$dayoweek<-weekdays(as.Date(data$date))
data<-data %>% mutate(dayoweek = ifelse(dayoweek == "Saturday" | dayoweek == "Sunday", "weekend", "weekday"))

data <-data %>% group_by(dayoweek, interval) %>% 
  mutate(average_steps2 = mean(finalsteps, na.rm = TRUE))

data %>% group_by(dayoweek) %>% summarise(mean = mean(average_steps2))

ggplot(data, aes(x=interval, y=average_steps2)) + geom_line() + facet_wrap(~dayoweek)
```

